\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

\usepackage{libertine}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{array}
\usepackage{graphicx}
\graphicspath{ {./images/} }

\usepackage{amsthm,amsmath,amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,shapes.geometric}

\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\pagestyle{plain}
\thispagestyle{empty}

\definecolor{carnellian}{RGB}{190,20,20}

\theoremstyle{definition}
\newtheorem{problem}{Problem}

\newcounter{subq}[problem]
\newenvironment{subproblem}
{\refstepcounter{subq} \begin{itemize} \item[(\alph{subq})]}
{\end{itemize} \medskip}
\DeclareMathOperator{\Ima}{Im}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Span}{Span}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Ann}{Ann}
\DeclareMathOperator{\Mat}{Mat}
%\DeclareMathOperator{\deg}{deg}



\usepackage{environ}
\NewEnviron{solution}[1][\vfill]{
    \textcolor{blue}{\BODY}
}

\newcommand{\hwnum}{6}
\newcommand{\duedate}{3/18/2025}
\renewcommand{\title}{Fields}

\begin{document}

\hspace{-10px}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textbf{Honors Algebra} & \textbf{Spring 2025} \\
    \textbf{HW \hwnum : \title} &  \textbf{\duedate} \\
\end{tabular*}

\vspace{1cm}

\textit{Abstract Algebra: An Integrated Approach by J.H. Silverman.}\\
Page 180-186: 7.14, 7.22, 7.29\\
Page 214-220: 8.3, 8.8, 8.21, 8.23\\
Page 320-325: 10.6, 10.12\\
Page 357-370: 11.2, 11.7, 11.8


\vspace{1cm}

%-----------TEMPLATE------------%
% \begin{problem}
%     \begin{enumerate}[label=(\alph*)]
%         \item 
%         \begin{solution}

%         \end{solution}

%         \item 
%         \begin{solution}

%         \end{solution}
%     \end{enumerate}
% \end{problem}

\begin{problem}[7.14]
    Let $R$ be a commutative ring.
    \begin{enumerate}[label=(\alph*)]
        \item Suppose that $a, b \in R$ have the property that $aR + bR = R$. 
              Prove that for all $m, n \geq 1$ we have 
              \[
                a^m R + b^n R = R
              \]
        \begin{solution}

        \end{solution}

        \item More generally, let $a_1, \ldots, a_t \in R$, and let $e_1, \ldots, e_t \geq 1$
              be positive integers. Prove that
              \[
                a_1 R + a_2 R + \cdots + a_t R = R \hspace{5px} \iff \hspace{5px} a_1^{e_1}R + a_2^{e_2}R + \cdots + a_t^{e_t}R = R
              \]
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[7.22]
    Let $R$ be a ring, let $P \subset R$ be a prime ideal, let $S = R \ P$ be the complement of $P$, let $R_S$
    be the localization ring as described in Exercise 7.21, and let
    \[
        Q = \{ (a, b) \in R_S : a \in P \}
    \]
    Prove that $Q$ is the unique maximal ideal of $R_S$. (A ring with a unique maximal ideal is called a local
    ring; see Exercise 3.53).

    \begin{solution}

    \end{solution}
\end{problem}

\begin{problem}[7.29]
    A polynomial $f(X_1, \ldots, X_n) \in F[X_1, \ldots, X_n]$ is said to be homogeneous of degree k if
    \[
        f(aX_1, \ldots, aX_n) = a^kf(X_1, \ldots, X_n) \hspace{5px} \text{for all } a \in F
    \]
    \begin{enumerate}[label=(\alph*)]
        \item Prove that $f$ is a homogeneous polynomial of degree $k$ if and only if $f$ is a sum of the form
              \[
                f(X_1, \ldots, X_n) = \sum_{\substack{i_1, i_2, \ldots, i_n \geq 0\\ i_1 + i_2 + \cdots + i_n = k}} c_{i_1, i_2, \ldots, i_n} X_1^{i_1} X_2^{i_2} \cdots X_n^{i_n}
              \]
        \begin{solution}

        \end{solution}

        \item Prove that the elementary symmetric polynomials $s_k (X_1, \ldots, X_n)$ described in Definition 7.40
              is a homogeneous polynomial of degree $k$.
        \begin{solution}

        \end{solution}

        \item Let $f(X_1, \ldots, X_n) \in F(X_1, \ldots, X_n)$ be homogeneous of degree $k$. Prove that
              \[
                X_1 \frac{\partial{f}}{X_1} + X_2 \frac{\partial{f}}{X_2} + \cdots + X_n \frac{\partial{f}}{X_n} = kf
              \]
              (\textit{Hint.} If you view
              \[
                f(TX_1, \ldots, TX_n) = T^k f(X_1, \ldots, X_n)
              \]
              as being a relation in the polynomial ring $F[T, X_1, \ldots, X_n]$, then you can differentiate it with
              respect to $T$. Then set $T = 1$.)
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[8.3]
    This exercise sketches a proof of the following result, which says that if a number is the root of 
    a polynomial in $Q[x]$, then it cannot be too closely approximated by rational numbers.

    \textbf{Theorem 8.46} Let $f(x) \in Q[x]$ be a polynomial ofdegree $d \geq 1$. There is a positive 
    constant $C_f > 0$ such that if $\alpha \in mathbb{C} \ \mathbb{Q}$ is a non-rational root of $f(x)$, then
    \[
        \Bigg| \frac{p}{q} - \alpha \Bigg| \geq \frac{C_f}{q^d} \hspace{5px} \text{for all } \frac{p}{q} \in \mathbb{Q}
    \]
    \begin{enumerate}[label=(\alph*)]
        \item Prove that every $p/q \in mathbb{Q}$ satisfies either
        \[
            f\bigg( \frac{p}{q} \bigg) = 0 \hspace{5px} \text{or} \hspace{5px} \Bigg| f\bigg( \frac{p}{q} \bigg) \Bigg| \geq \frac{1}{q^d}
        \]
        \begin{solution}

        \end{solution}

        \item Let $g(x) \in \mathbb{C}[x]$ be a polynomial of degree $e$, and let $\alpha \in \mathbb{C}$. Prove that there
              is a constant $A_{g, \alpha}$ so that
              \[
                |g(\beta)| \leq A_{g, \alpha} \max\{1, |\beta - \alpha|^e\} \hspace{5px} \beta \in \mathbb{C}
              \]
            (\textit{Hint.} Expand $g(x)$ as a sum of powers of $x - \alpha$)
        \begin{solution}

        \end{solution}

        \item Use (a) and (b) to prove Theorem 8.46. (\textit{Hint.} Since we are given that $f(\alpha) = 0$),
              we can factor $f(x)$ as $f(x) = (x - \alpha)g(x)$ for some $g(x) \in \mathbb{C}[x]$.)
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[8.8]
    Let $F$ be a finite field of order $q$, and assume that $q$ is odd.
    \begin{enumerate}[label=(\alph*)]
        \item Let $a, b \in F*$. If $a^2 = b^2$, prove that either $a = b$ or $a = -b$.
        \begin{solution}

        \end{solution}

        \item Show by way of an example that (a) is not true for the rings $\mathbb{Z}/8\mathbb{Z}$
              and $\mathbb{Z}/15\mathbb{Z}$.
        \begin{solution}

        \end{solution}

        \item Let 
        \[
            \mathcal{R} = \{ a^2 : a \in F* \} \hspace{5px} \text{and} \hspace{5px} \mathcal{N} = \{ b \in F* : b \not\in \mathcal{R} \}
        \]
        be, respectively, the set of squares and non-squares in $F*$. Prove that $\mathcal{R}$ and $\mathcal{N}$ each contain
        exactly $(q - 1)/2$ distinct elements.
        \begin{solution}

        \end{solution}

        \item Let $f(x)$ be the polynomial
              \[
                f(x) = x^{\frac{q-1}{2}} - 1
              \]
              Prove that $\mathcal{R}$ is exactly the set of roots of $f(x)$ in $F$. (\textit{Hint.} Use Lagrange
              to prove that the elements of $\mathcal{R}$ are roots. Then use (c) and Theorem 8.8(c).)
        \begin{solution}

        \end{solution}

        \item Let $c \in F*$. Prove that
              \[ 
                c^{\frac{q-1}{2}} \equiv 
                \begin{cases} 
                    1 & \text{if } c \in \mathcal{Q}\\
                    -1 & \text{if } c \in \mathcal{N}
                \end{cases}
              \]
              (\textit{Hint.} Lagrange says that every element of $F*$ is a root of $x^{q-1} - 1$.
              Factor this polynomial as $f(x)g(x)$ and use (d).)
        \begin{solution}

        \end{solution}

        \item Let $a_1, a_2 \in \mathcal{R}$ and $b_1, b_2 \in \mathcal{N}$. Prove that
              \[
                a_1a_2 \in \mathcal{R} \hspace{5px} \text{and} \hspace{5px} b_1b_2 \in \mathcal{R}
              \]
              The first of these facts is hardly surprising, since indeed, the product of two squares is
              a square in any commutative ring. But the second fact is surprising, since in most rings, 
              most products of non-square won't be squares. 
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[8.21]
    Let $\Phi_{1}(x) = x - 1$, and for $n /geq 1$, define the $n$th cyclotomic polynomial $\Phi_n(x)$ inductively by the formula
    \[
        x^n - 1 = \prod_{m|n}\Phi_m(x)
    \]
    as described in Definition 8.37.
    \begin{enumerate}[label=(\alph*)]
        \item Compute $\Phi_n(x)$ for all $2 \leq n \leq 10$.
        \begin{solution}

        \end{solution}

        \item Let $\zeta_n = e^{2\pi i/n} \in \mathbb{C}$ be a primitive $n$th-root of unity. Prove that $\Phi_n(x)$ factors in $\mathbb{C}[x]$ as
              \[
                    \Phi_n(x) = \prod_{\substack{1\leq d \leq d\\ \gcd(d, n)=1}}(x - \zeta^d_n)
              \]
              Thus $\Phi_n(x)$ is a monic polynomial in $\mathbb{C}[x]$.
        \begin{solution}

        \end{solution}

        \item Prove that all the coefficients of $\Phi_n(x)$ are in $\mathbb{Z}$.
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[8.23]
    Let $R$ be a PID with fraction field $K$, let $\pi \in R$ be an irreducible element, and let
    \[
        f(x) = c_0 = c_1x + \cdots + c_dx^d \in R[x]
    \]
    be a polynomial whose coefficients satisfy
    \[
        \pi \not| c_d, \quad \pi | c_i \text{ for } 0 \leq i < d, \quad \text{ and } \pi^2 \not| c_0
    \]
    Prove that $f(x)$ is irreducible in $K[x]$.
    
    \begin{solution}

    \end{solution}
\end{problem}

\begin{problem}[10.6]
    Let $V$ be the $\mathbb{R}$-vector space of polynomials of degree at most 3,
    \[
        V = \{ a + bx + cx^2 + dx^3 : a, b, c, d \in \mathbb{R} \}
    \]
    \begin{enumerate}[label=(\alph*)]
        \item Prove that the following sets are $\mathbb{R}$-bases for $L$:
        \[
            \text{(i) } \mathcal{A} = \{ 1, x, x^2, x^3 \} \quad \quad \text{(ii) } \mathcal{B} = \{ 1, x + 1, (x + 1)^2, (x + 1)^3 \}
        \]
        \begin{solution}

        \end{solution}

        \item Let $L : V \longrightarrow V$ be differentiation: i.e.,
              \[
                    L : V \longrightarrow V, \quad L(a + bx + cx^2 + dx^3) = b + 2cx + 3dx^2
              \]
              Using the bases in (a), compute the following matrices associated to $L$:
              \[
                    \text{(i) } \mathcal{M}_{L, \mathcal{A}, \mathcal{A}} \quad \quad \text{(ii) } \mathcal{M}_{L, \mathcal{B}, \mathcal{A}}
              \]
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[10.12]
    Let $V$ be a finite-dimensional vector space, and let $L \in \End_F(V)$. Prove that the following are equivalent:
    \begin{enumerate}[label=(\alph*)]
        \item There is an $L_1 \in \End_F(V)$ satisfying $LL_1 = I$. (We say that $L_1$ is a right-inverse)
        \item There is an $L_2 \in \End_F(V)$ satisfying $L_2L = I$. (We say that $L_2$ is a left-inverse)
    \end{enumerate}
    N.B. Be sure that you use the hypothesis that $V$ is finite dimensional, since the statement is false for infinite-dimensional vector spaces.
    
    \begin{solution}

    \end{solution}
\end{problem}

\begin{problem}[11.2]
    Let $R$ be a ring, and let $a_1, \ldots, a_n \in R$. We define an evaluation map
    \[
        E_a : R[x] \longrightarrow R^n, \quad E_a(f(x)) = (f(a_1), \ldots, f(a_n))
    \]
    \begin{enumerate}[label=(\alph*)]
        \item Prove that $E_a$ is an $R$-module homomorphism
        
        \begin{solution}

        \end{solution}

        \item Suppose that $R$ is an integral domain. Prove that the kernel of $E_a$ is a principal ideal of $R[x]$. Find a generator for this ideal.
        
        \begin{solution}

        \end{solution}

        \item Is (b) true if we drop the assumption that $R$ is an intergral domain?
        
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[11.7]
    THis exercise asks you to generalize Propostiion 11.18. Let $M$ be an $R$-module. For each ideal $I$ of $R$, we define $IM$ to be the set
    \[
        IM = \{ a_1m_1 + \cdots + a_km_k : k \geq 0, a_1, \ldots, a_k \in I, m_1, \ldots, m_k \in M \}
    \]
    \begin{enumerate}[label=(\alph*)]
        \item Prove that $IM$ is a submodule of $M$.
        
        \begin{solution}

        \end{solution}

        \item Prove that the quotient module $M/IM$ has a natural structure as an $R/I$-module.
        
        \begin{solution}

        \end{solution}

        \item More generally, let $J \subseteq I$ be ideals of $R$, and let $K$ be the set
              \[
                    K =\{ r \in R : rI \subseteq J \}
              \]
            Prove that $K$ is an ideal of $R$, that $JM$ is a submodule of $IM$, and that the quotient $IM/JM$ is naturally an $R/K$-module.
        
        \begin{solution}

        \end{solution}

        \item Suppose that $R$ is an integral domain, and suppose that the ideals $I$ and $J$ in (c) are principal, say $I = aR$ and $J = bR$. Prove that $b = ac$ for some $c \in R$ and that the ideal $K$ defined in (c) is the principal ideal $cR$.
        
        \begin{solution}

        \end{solution}
    \end{enumerate}
\end{problem}

\begin{problem}[11.8]
    Let $M$ be a finitely generated free $R$-module, and let $J$ be a maximal ideal of $R$. Prove that 
    \[
        \rank_R(M) = \dim_{R/J}(M/JM)
    \]
    Explain why this equality gives an alternative proof of Theorem 11.27; i.e., explain why it implies that every basis of $M$ has the same number of elements. (See Exerecise 11.7 for the definition of the submodule $JM$)
    
    \begin{solution}

    \end{solution}
\end{problem}

\end{document}